---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# rutledge

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/rutledge)](https://CRAN.R-project.org/package=rutledge)
<!-- badges: end -->

`{rutledge}` is an R data package that provides real-time PCR raw fluorescence
data by Rutledge et al. (2004) in tidy format.

The eponymous data set `rutledge` comprises a six-point, ten-fold dilution
series repeated in 5 independent runs. In each run, for each concentration there
are four replicates. Of a total of 240 amplification curves, 212 curves are 45
cycles long and 28 curves are 35 cycles long only. The data is for two targets
(amplicons): K1/K2, 102 bp, and K3/K2, 218 bp.

## Installation

Install `{rutledge}` from CRAN:

``` r
# Install from CRAN
install.packages("rutledge")
```

You can install the development version of `{rutledge}` like so:

``` r
# install.packages("remotes")
remotes::install_github("ramiromagno/rutledge")
```

## Data

`rutledge` is provided as a tidy data set, in long format, i.e. each row is
for an amplication curve point (cycle/fluor).

```{r}
library(rutledge)
rutledge
```

The `rutledge` data set comprises 240 amplification curves: 2 amplicons $\times$ 
5 runs (plates) $\times$ 6 dilution levels $\times$ 4 replicates.

```{r dpi=300, fig.width=8, fig.height=8}
rutledge |>
  dplyr::count(plate, target, copies, replicate)

rutledge |>
  ggplot(mapping = aes(
    x = cycle,
    y = fluor,
    group = interaction(plate, target, copies, replicate),
    col = as.character(copies)
  )) +
  geom_line(linewidth = 0.2) +
  geom_point(size = 0.2) +
  labs(y = "Raw fluorescence", colour = "No. of copies", title = "Six-point 10-fold dilution series") +
  guides(color = guide_legend(override.aes = list(linewidth = 0.5), reverse = TRUE)) +
  facet_grid(rows = vars(plate), cols = vars(target))
```

## Code of Conduct

Please note that the rutledge project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## References

R. G. Rutledge. _Sigmoidal curve-fitting redefines quantitative real-time PCR with the prospective of developing automated high-throughput applications_. Nucleic Acids Research 32:e178 (2004). doi: [10.1093/nar/gnh177](https://doi.org/10.1093/nar/gnh177).
